\hypertarget{namespacemain__paper}{}\section{main\+\_\+paper Namespace Reference}
\label{namespacemain__paper}\index{main\+\_\+paper@{main\+\_\+paper}}


Created on Wed Feb 28 09\+:47\+:22 2018 Author Alejandro Pena-\/\+Bello \href{mailto:alejandro.penabello@unige.ch}{\tt alejandro.\+penabello@unige.\+ch} Main script used for the paper Optimization of P\+V-\/coupled battery systems for combining applications\+: impact of battery technology and location (Pena-\/\+Bello et al 2018 to be published).  




\subsection{Detailed Description}
Created on Wed Feb 28 09\+:47\+:22 2018 Author Alejandro Pena-\/\+Bello \href{mailto:alejandro.penabello@unige.ch}{\tt alejandro.\+penabello@unige.\+ch} Main script used for the paper Optimization of P\+V-\/coupled battery systems for combining applications\+: impact of battery technology and location (Pena-\/\+Bello et al 2018 to be published). 

The study focuses on residential P\+V-\/coupled battery systems. We study the different applications which residential batteries can perform from a consumer perspective. Applications such as avoidance of PV curtailment, demand load-\/shifting and demand peak shaving are considered along with the base application, PV self-\/consumption. Moreover, six different battery technologies currently available in the market are considered as well as three sizes (3 k\+Wh, 7 k\+Wh and 14 k\+Wh). We analyze the impact of the type of demand profile and type of tariff structure by comparing results across dwellings in Switzerland and in the U.\+S. The battery schedule is optimized for every day (i.\+e. 24 h optimization framework), we assume perfect day-\/ahead forecast of the electricity demand load and solar PV generation in order to determine the maximum economic potential regardless of the forecast strategy used. Aging was treated as an exogenous parameter, calculated on daily basis and was not subject of optimization. Data with 15-\/minute temporal resolution were used for simulations. The model objective function have two components, the energy-\/based and the power-\/based component, as the tariff structure depends on the applications considered, a boolean parameter activate the power-\/based factor of the bill when is necessary. Every optimization was run for one year and then the results were linearly-\/extrapolated to reach the battery end of life. Therefore, the analysis is done with same prices for all years across battery lifetime. We assume 30\% of capacity depletion as the end of life. The script works in Linux and Windows This script works was tested with pyomo version 5.\+4.\+3 \subsubsection*{I\+N\+P\+U\+TS }

\subsubsection*{O\+U\+T\+P\+U\+TS }

\subsubsection*{T\+O\+DO }

User Interface, including path to save the results and choose countries, load curves, etc. Simplify by merging select\+\_\+data and load\+\_\+data and probably load\+\_\+param. \subsubsection*{Requirements }

Pandas, numpy, sys, glob, os, csv, pickle, functools, argparse, itertools, time, math, pyomo and multiprocessing 